---
title: "R Notebook"
output:
  html_notebook: toc:True code_folding:True
  pdf_document: default
---
# Introduction

This is an introduction course to R- programming for those who have basics of statistics and any other programming language.


#Loading the Libraries 
 In every project that you a=under take as a data analyst/scientist, it's important to note the packages that `tools` that you will need in the course of the analysis, or creating your models.
 -Hence my opinion is that you load all the required libraries at the initial stage of your  project.

```{r, message=FALSE, warning=FALSE}

library(dplyr)
library(ggplot2)
library(lubridate)
library(tidyverse)

```
## Loading the Datasets 

```{r}
train <- read.csv("E:/Rstaff/kaggle/titanic/train.csv",na.strings=c('NA',''))
test <- read.csv("E:/Rstaff/kaggle/titanic/test.csv",na.strings=c('NA',''))
```
## Data Exploration
```{r}
dim(train)
dim(test)
```

```{r}
glimpse(tr)
```
## Data manupulation

```{r}
tr<-train %>% mutate(Survived= as.factor(Survived),
                     Pclass=as.factor(Pclass),
                     SibSp=as.factor(SibSp))
```


```{r}
s<-na.omit(tr$Age)
```


```{r}
ggplot(tr, aes(Sex, Age))+
  geom_boxplot( aes(fill= Sex))
```
```{r}
ggplot(tr, aes(Embarked, Age))+
  geom_boxplot(aes(fill= Embarked))

```

```{r}
levels(tr$Sex)

sum(is.na(tr$Age))
```
```{r}
head(subset(tr, Sex=="male" & Age >= 40 & Embarked=="C"))
```



```{r}
head(tr)
```

```{r}
ggplot(tr, aes(Pclass))+
  geom_bar(aes(fill= Survived))


```
```{r}

qplot(Pclass, data = tr,fill= Survived, position = "dodge")
 
```
```{r}
summary(tr)
```
```{r}
tr %>% group_by(na.omit(tr$Embarked)) %>% 
  count()
```









